### 2018-03-25 Graduate - Introduction to Analysis II/HW5/5HW20180313.tex
update problem 6

@@

\textbf{Sol.}

>>>>

Properties: first, by Theorem 3.6, notice $f$ has one zero $z = 0$ and no poles,
$$
g(0) = \frac{1}{2\pi i}\int_{\gamma}\frac{zf'(z)}{f(z)}dz = \sum_{i=1}^{n}z_i n(\gamma; z_i) - \sum_{j=1}^{m}p_i n(\gamma, p_j) = 0.
$$

@@

\textbf{Sol.} A very trivial version is: change $\gamma$ to any closed rectifiable curve in G where $f, g$ are meromorphic in a neighbourhood of $G$ with no zeros or poles in $\gamma$. In this case we do not need to modify the proof.
